No Correlations were Found between the efforts made by the Staff of Toronto's Central Intake Line and Toronto;s Homeless Death Counts

### 2024-01-22 outputs/paper/paper.qmd
editted and created citations in the reference.bib file

library(tidyverse)
library(palmerpenguins)
library(dplyr)
library(lubridate)
library(zoo)
```

@@

```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false

ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = "none") +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

>>>>

library(tidyverse)
library(dplyr)
library(lubridate)
library(zoo)
```

@@

```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false
ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = "none") +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```
